SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-20 paper.tex
review ACHIEVEMENTS

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13}, CUDA programs~\cite{Pereira15}, and Qt-based consumer electronics applications~\cite{Sousa15}. Other SMT-based BMC approaches have also been proposed and implemented~\cite{MerzFS12}, but the coverage and verification time of all existing approaches are still limited for specific class of programs, especially for those that contain floating-point arithmetic and manipulate the heap~\cite{BeyerSVCOMP15}.

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro {\it et al.} was further developed to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering partial-order reduction and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Such approach was also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer, in standard benchmarks, which were later confirmed by the benchmarks' creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC)~\cite{CordeiroF11,Cordeiro12}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prunes the state space exploration~\cite{Inverso14,civl15}. However, the class of concurrent (embedded systems) programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited.

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated, which demonstrate its effectiveness in some real-life embedded systems applications~\cite{Gadelha15,Rocha15,Brain15}. However, the main challenge still remains to compute and strengthen loop invariants to prove program correctness and timeliness. Invariant generation algorithms have substantially evolved over the years to efficiently discover inductive invariants of programs~\cite{pips:2013,Henry:2012} or to continuously refine them~\cite{Beyer15}. However, there is still a lack of studies for exploiting the combination of different invariant generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities), in order to ensure system robustness w.r.t. implementation aspects.

@@

Lastly, yet importantly, BMC tools like CBMC~\cite{Clarke04}, ESBMC~\cite{MorseCNF13,MorseRCN014}, and LLBMC~\cite{MerzFS12} represent the most prominent ones for verifying C programs, as observed in the Intl. Competition on Software Verification~\cite{BeyerSVCOMP15}.

@@

>>>>

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13}, CUDA programs~\cite{Pereira15}, and Qt-based consumer electronics applications~\cite{Sousa15}. Such approach was also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer, in standard benchmarks, which were later confirmed by the benchmarks' creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC)~\cite{CordeiroF11,Cordeiro12}. Other SMT-based BMC approaches have also been proposed and implemented~\cite{MerzFS12}, but the coverage and verification time of all existing BMC approaches are still limited for specific class of programs, especially for those that contain intensive floating-point arithmetic and dynamic memory allocation~\cite{BeyerSVCOMP15}. One possible research direction is to bridge the gap between BMC tools and SMT solvers to develop more efficient decision procedures to handle specific class of programs.

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro {\it et al}. was further developed to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state space exploration~\cite{Inverso14,civl15}. However, the class of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores with the goal to remove redundant behaviour.

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated in the literature, which demonstrate its effectiveness in some real-life embedded systems applications~\cite{Gadelha15,Rocha15,Brain15}. However, the main challenge still remains open, {\it i.e.}, to compute and strengthen loop invariants to prove program correctness and timeliness in a more efficient and effective way in order to be competitive with other model checking approaches. In particular, invariant generation algorithms have substantially evolved over the last years to discover inductive invariants of programs~\cite{pips:2013,Henry:2012} or to continuously refine them during verification~\cite{Beyer15}. However, there is still a lack of studies for exploiting the combination of different invariant generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities) and how to strengthen them during verification, in order to ensure system robustness w.r.t. implementation aspects.

@@

Lastly, yet importantly, BMC tools like CBMC~\cite{Clarke04}, ESBMC~\cite{MorseCNF13,MorseRCN014}, and LLBMC~\cite{MerzFS12} represent the most prominent ones for verifying C programs, as observed in the Intl. Competition on Software Verification~\cite{Beyer14,BeyerSVCOMP15}.

@@

\bibitem{KahlonWG09}
Kahlon V, Wang C, Gupta A.
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order
  Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.
